Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2016-07-04 ijar-npb-ms.tex
Lemma 3 statement sharpened.
revert to 'cases' at end of sec 7.2.2

In this example, the theory presented in Section \ref{sec:setsofrel} enabled avoiding numerical optimisation
for 91.9\% and 95.7\% of the $301$ considered time points for $\lRsys(\cdot)$ and $\uRsys(\cdot)$, respectively.
Further detail is in Appendix \ref{ap:needtoopt}.

@@

Figure \ref{fig:need-to-opt-8} shows the changing worst case probability (subject to $|y-p|>0.1$) that optimisation will be required over time for the actual choice of prior and the values of $m, N, \nu$ and $\nl$ in the brake example from the main body of the paper.  Note in particular that when $m=1$, Lemma 3 *** always applies and optimisation is never required.  This is true for all values of $N$ and $y$.

>>>>

In this example, the theory presented in Section \ref{sec:setsofrel} enabled avoiding numerical optimisation
in 91.9\% of cases for $\lRsys(\cdot)$ and in 95.7\% of cases for $\uRsys(\cdot)$.
Further detail is in Appendix \ref{ap:needtoopt}.

@@

Figure \ref{fig:need-to-opt-8} shows the changing worst case probability (subject to $|y-p|>0.1$) that optimisation will be required over time for the actual choice of prior and the values of $m, N, \nu$ and $\nl$ in the brake example from the main body of the paper.  Note in particular that when $m=1$, Lemma 3 always applies for $y \in (0,1)$ and so optimisation is never required.  This is true for all values of $N$ and $y$.
